A Memory-Bounded, Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-02-24 05-conclusion.tex
Coloca a conclusão no passado

We propose a small-step structural operational semantics for \CEU and a proof
that reactions are deterministic, terminate in finite time, and use bounded
memory, i.e., that for a given arbitrary timeline of input events, multiple
executions of the same program always react in bounded time and arrive at the
same final finite memory state.

>>>>

In this paper, we proposed a small-step structural operational semantics for
\CEU and proved that under it reactions are deterministic, terminate in
finite time, and use bounded memory, i.e., that for a given arbitrary
timeline of input events, multiple executions of the same program always
react in bounded time and arrive at the same final finite memory state.
